Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-16 ms.tex
clean-up

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}

@@

\section{Introduction}
%why dust important in astronomy/astrophysics
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. At mid-infrared
and far-infrared wavelengths, Galactic dust emission is a major contributor
to the observed sky intensity. In the optical and ultraviolet, extinction
by foreground dust grains attenuates the signal from extragalactic sources
over the entire sky. Understanding the properties of dust in the interstellar 
medium (ISM) is valuable in its own right, as the ISM is the site of star 
formation, thereby playing a crucial role in galaxy evolution. Equally, or 
perhaps even more important to the practice of astronomy, however, is 
accurately accounting for dust as a foreground which reddens optical/UV o
bservations and superimposes Galactic emission on low-frequency observations 
of the cosmic microwave background (CMB). 
%specify ``low frequency more precisely eventually
% somewhere mention re-radiation

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. IRAS, with its $\sim$6$'$ 
resolution, revolutionized the study of Galactic dust emission, first revealing
 the high-latitude ``infrared cirrus'' using \IRAS~60$\mu$m and 100$\mu$m 
observations \citep{low84, wheelock94}. Beginning in 1989, DIRBE  mapped the 
full sky at ten infrared wavelengths from 1.25$\mu$m to 240$\mu$m with a 
reliable zero point, but inferior 0.7$^{\circ}$ angular resolution 
\citep{boggess92}.mention FIRAS specifically, since it is important to FDS99.

FDS99 used FIRAS \citep{firas} to make a globally best-fit model of dust 
emission appropriate over a very broad range of frequencies. They showed that 
a model consisting of a single MBB with power law index $\beta$ 
could not fit the IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a spectrum consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
silicates and carbonaceous grains.

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of their superb, 
relatively artifact-free broadband data covering the entire sky and a broad 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example \AKARI~140-160$\mu$m. We also 
anticipate the optical depth map we derive will be useful as a comparison for 
extinction estimates based directly upon optical/NIR observations of stars.

@@

In $\S$\ref{sec:data} we discuss the data used in throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
dust emission model we fit to the \PLANCK and \IRAS~data. In 
$S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
we use to estimate the parameters of our model. In $\S$\ref{sec:results} we 
present the full-sky maps of dust temperature and optical depth we have 
obtained, and conclude and $\S$\ref{sec:conclusion}

@@

@@

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
143 GHz) were not used in our fit, while the four lowest-frequency data
points were not used in the \cite{planckdust} fit.}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature. Note the differing colorscales.
Both models incorporating \PLANCK~data clearly show a major improvement in 
resolution relative to SFD.}
\end{center}
\end{figure}

>>>>

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}
\newcommand{\FIRAS}{{\it FIRAS}}

@@

\section{Introduction}
%why dust important in astronomy/astrophysics
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission is a major contributor
to the observed sky intensity. At optical and ultraviolet wavelengths, 
extinction by foreground dust grains attenuates the signal from extragalactic 
sources over the entire sky. Understanding the properties of dust in the 
interstellar medium (ISM) is valuable in its own right, as the ISM is the site 
of star formation, thereby playing a crucial role in galaxy evolution. Equally,
 or perhaps even more important to the practice of astronomy, however, is 
accurately accounting for dust as a foreground which reddens optical/UV o
bservations and superimposes Galactic emission on low-frequency observations 
of the cosmic microwave background (CMB). 
%specify ``low frequency more precisely eventually
% somewhere mention re-radiation

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. \IRAS, with its $\sim$4$'$ 
resolution, revolutionized the study of Galactic dust emission, first revealing
 the high-latitude ``infrared cirrus'' using 60$\mu$m and 100$\mu$m 
observations \citep{low84, wheelock94}. Then, beginning in 1989, DIRBE provided
complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
with a reliable zero point \citep{boggess92}. COBE/\FIRAS~\citep{firas} also 
provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 
narrow frequency bins between 200 GHz and 2100 GHz.

\cite{FDS99} (hereafter FDS99) used \FIRAS~data to derive a globally best-fit 
model of dust emission applicable over a very broad range of frequencies. 
FDS99 showed that a model consisting of a single MBB with power law index 
$\beta$ 
could not accurately match the \IRAS/\FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a dust emission model consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
amorphous silicates and carbonaceous grains.

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a broad 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ resolution maps of dust temperature and optical 
depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, e expect our best-fit parameters to be useful in constructing high-resolution
 predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also data near the peak of the dust SED, for
 example \AKARI~140-160$\mu$m. We also anticipate our derived optical depth map
 will serve as a useful comparison for extinction estimates based 
directly upon optical/NIR observations of stars.

@@

In $\S$\ref{sec:data} we discuss the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
dust emission model we fit to the \PLANCK and \IRAS~data. In 
$S$\ref{sec:fitting} we provide details of the Markov Chain Monte Carlo method 
with which we have estimated the parameters of our model. In 
$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
optical depth thus obtained, and conclude and $\S$\ref{sec:conclusion}

@@

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
143 GHz) were not used in our fit, while the three lowest-frequency data
points were not used in the \cite{planckdust} fit.}
\end{center}
\end{figure}

@@

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$). Note the differing colorscales.
Both models incorporating \PLANCK~data clearly show a major improvement in 
resolution relative to SFD.}
\end{center}
\end{figure}
